Perturbation theories in the complex plane

### 2020-06-28 SlideToulouse/main.tex
minor corrections on slides

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering
Full Configuration Interaction gives us access to high order terms of the perturbation series !
\end{beamerboxesrounded}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{gill1986.png}
    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using STO-3G basis set MPn theory (n~=~1-20).}
    \label{fig:my_label}
\end{figure}

@@

\footnotetext{\tiny{Gill et al. Why does unrestricted Møller–Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}

@@

    \item Infinitely differentiable on $\mathbb{R}$
\end{itemize}

@@

\begin{frame}{And if we look in the complex plane ?}

@@

\centering The function has 4 singularities in the complex plane !

@@

\begin{frame}{Which features of the system localize the singularities ?}

\begin{itemize}
    \item Partitioning of the Hamiltonian: Møller-Plesset, Epstein-Nesbet,...
    \item Zeroth order reference: weak correlation or strongly correlated electrons.
    \item Finite or complete basis set.
    \item Localized or delocalized basis functions.
\end{itemize}

@@

\begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\alpha$}
\begin{itemize}
    \item Large avoided crossing
    \item Non-zero imaginary part
    \item Interaction with a low lying doubly excited states
\end{itemize} 
\end{beamerboxesrounded}

@@

\begin{itemize}
    \item $E_{kin} >> E_p$
    \item Uniform density of electrons
    \item \textcolor{red}{Weak correlation}
\end{itemize}

@@

\begin{itemize}
    \item $E_{kin} << E_p$
    \item Electrons on the opposite sides of the sphere
    \item \textcolor{red}{Strong correlation}
    \end{itemize}

>>>>

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering
Full Configuration Interaction gives access to high-order terms of the perturbation series!
\end{beamerboxesrounded}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{gill1986.png}
    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
    \label{fig:my_label}
\end{figure}

@@

\footnotetext{\tiny{Gill et al. Why does unrestricted M{\o}ller-Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}

@@

    \item Infinitely differentiable in $\mathbb{R}$
\end{itemize}

@@

\begin{frame}{And if we look in the complex plane?}

@@

\centering The function has 4 singularities in the complex plane!

@@

\begin{frame}{Which features of the system localize the singularities?}

\begin{itemize}
    \item Partitioning of the Hamiltonian: Møller-Plesset, Epstein-Nesbet, \ldots
    \item Zeroth-order reference: weak or strong correlation.
    \item Finite or complete basis set.
    \item Localized or delocalized basis functions.
\end{itemize}

@@

\begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\alpha$}
\begin{itemize}
    \item Large avoided crossing
    \item Non-zero imaginary part
    \item Interaction with a low-lying doubly excited states
\end{itemize} 
\end{beamerboxesrounded}

@@

\begin{itemize}
    \item $E_\text{kin} \gg E_\text{pot}$
    \item Uniform density of electrons
    \item \textcolor{red}{Weak correlation}
\end{itemize}

@@

\begin{itemize}
    \item $E_\text{kin} \ll E_\text{pot}$
    \item Electrons on the opposite sides of the sphere
    \item \textcolor{red}{Strong correlation}
    \end{itemize}
